Covid-19 A Spatio-Temporal Investigation.

### 2021-01-03 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 At the end of 2019, the situation regarding infections by Covid-19 *(Sars-Cov-2)* was already a cause of concern, and it was considered an epidemic in the city of Wuhan in China $\!\!^1$, although it was difficult to identify the virus' origin, since the Severe Acute Respiratory Syndrome *(SARS)* and the Middle East respiratory syndrome *(MERS)* usually need intermediate hosts $\!\!^2$, there is a possibility that bats and pangolins were the first carriers. After several public organizations advised governments to have caution relating to Covid-19, on March 12 of 2020 the pandemic state was recognized by the World Health Organization *(WHO)* $\!\!^3$.

>>>>

 At the end of 2019, the situation of infections by Covid-19 *(Sars-Cov-2)* was already a cause for concern, and it was considered an epidemic in the city of Wuhan in China $\!\!^1$, although it was difficult to identify the virus' origin, it's known that the Severe Acute Respiratory Syndrome *(SARS)* and the Middle East respiratory syndrome *(MERS)* usually need intermediate hosts $\!\!^2$, there is a possibility that bats and pangolins were the first carriers. After several public organizations called for caution relating to Covid-19, on March 12 of 2020 the pandemic state was recognized by the World Health Organization *(WHO)* $\!\!^3$.
